Abstract Binding Trees

### 2015-10-22 paper.tex
Elaborate a bit on the Grothendieck construction

\newcommand\ParamsOf{\pi_\mathfrak{p}}
\newcommand\ArityOf{\pi_\mathfrak{a}}
\newcommand\Sets{\mathbf{Set}}
\newcommand\SCtx{\mathbf{SCtx}}

@@

Then, fix a covariant presheaf of operators
$\Operators:\SCtx\times\Arities\to\Sets$ such that the arrows in $\SCtx$ lift to
renamings of operators' parameters. Via the Grothendieck
construction\footnote{Category of elements.} $\Grothendieck{}{}$ on the operator
presheaf $\Operators$ we also have a category with objects
$\Member{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{\varrho}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{\varrho'}}{\vartheta'}}$
for $f : \Pair{\Upsilon}{\varrho}\to\Pair{\Upsilon'}{\varrho'}$ such that
$\EqMember{\Restriction{f}\vartheta}{\vartheta'}{\Operators\Pair{\Upsilon'}{\varrho'}}$.

>>>>

\newcommand\ParamsOf{\pi_\mathfrak{p}}
\newcommand\ArityOf{\pi_\mathfrak{a}}
\newcommand\Cats{\mathbf{Cat}}
\newcommand\Sets{\mathbf{Set}}
\newcommand\SCtx{\mathbf{SCtx}}

@@

Then, fix a covariant presheaf of operators
$\Operators:\SCtx\times\Arities\to\Sets$ such that the arrows in $\SCtx$ lift to
renamings of operators' parameters. Via the Grothendieck
construction\footnote{In this case, $C\Grothendieck{}{\Psi}$ represents the
  category of elements of a copresheaf $\Psi : C\to\Sets$ but we keep the $C$
  implicit and simply refer to it as the Grothendieck construction.
  Alternatively, this construction can be understood as a coend
  $C\Grothendieck{}{\Psi} \cong \int^{c \in C}c / C \otimes |\Psi(c)|$.}
$\Grothendieck{}{(-)} : \Sets^{C}\to\Cats$ on operators we have a category of
objects
$\Member{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Grothendieck{}{\Operators}}$
for $\Member{\vartheta}{\Operators\Pair{\Upsilon}{\varrho}}$ and morphisms
$\Hom{\Grothendieck{}{\Operators}}{\Pair{\Pair{\Upsilon}{\varrho}}{\vartheta}}{\Pair{\Pair{\Upsilon'}{\varrho'}}{\vartheta'}}$
for $f : \Pair{\Upsilon}{\varrho}\to\Pair{\Upsilon'}{\varrho'}$ such that
$\EqMember{\Restriction{f}\vartheta}{\vartheta'}{\Operators\Pair{\Upsilon'}{\varrho'}}$.
